Generating Random Logic Programs Using Constraint Programming

### 2020-01-21 paper/phase_transition.tex
Another plot

% Created by tikzDevice version 0.12.3 on 2020-01-20 17:11:57
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 34.79, 30.69) rectangle (428.12,139.04);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 34.79, 30.69) rectangle (428.12,139.04);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79, 84.06) --
	(428.12, 84.06);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,114.41) --
	(428.12,114.41);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 34.79,122.88) --
	(428.12,122.88);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79, 30.69) --
	(428.12, 30.69);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.79,102.78) --
	(428.12,102.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 30.69) --
	( 47.60,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 30.69) --
	( 60.73,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 30.69) --
	( 73.86,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 30.69) --
	( 86.99,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 30.69) --
	(100.13,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 30.69) --
	(113.26,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 30.69) --
	(126.39,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 30.69) --
	(139.53,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 30.69) --
	(152.66,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 30.69) --
	(165.79,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 30.69) --
	(178.92,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 30.69) --
	(192.06,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 30.69) --
	(205.19,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 30.69) --
	(218.32,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 30.69) --
	(231.46,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 30.69) --
	(244.59,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 30.69) --
	(257.72,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (270.85, 30.69) --
	(270.85,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (283.99, 30.69) --
	(283.99,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (297.12, 30.69) --
	(297.12,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (310.25, 30.69) --
	(310.25,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (323.39, 30.69) --
	(323.39,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (336.52, 30.69) --
	(336.52,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (349.65, 30.69) --
	(349.65,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (362.78, 30.69) --
	(362.78,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (375.92, 30.69) --
	(375.92,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (389.05, 30.69) --
	(389.05,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (402.18, 30.69) --
	(402.18,139.04);

\path[draw=drawColor,line width= 0.6pt,line join=round] (415.32, 30.69) --
	(415.32,139.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 82.72) --
	( 47.60,103.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 47.60, 52.70) --
	( 47.60, 41.88) --
	( 47.60, 25.23) --
	( 47.60,  0.00);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 42.67, 82.72) --
	( 42.67, 52.70) --
	( 47.60, 52.70) --
	( 52.52, 52.70) --
	( 52.52, 82.72) --
	( 47.60, 82.72) --
	( 42.67, 82.72) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 42.67, 67.97) --
	( 47.60, 67.97) --
	( 52.52, 67.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 85.45) --
	( 60.73,106.72);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 60.73, 52.70) --
	( 60.73, 36.00) --
	( 60.73,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 55.80, 85.45) --
	( 55.80, 52.70) --
	( 60.73, 52.70) --
	( 65.65, 52.70) --
	( 65.65, 85.45) --
	( 60.73, 85.45) --
	( 55.80, 85.45) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 55.80, 68.54) --
	( 60.73, 68.54) --
	( 65.65, 68.54);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 85.83) --
	( 73.86,107.32);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 73.86, 51.92) --
	( 73.86, 34.23) --
	( 73.86,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 68.94, 85.83) --
	( 68.94, 51.92) --
	( 73.86, 51.92) --
	( 78.79, 51.92) --
	( 78.79, 85.83) --
	( 73.86, 85.83) --
	( 68.94, 85.83) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 68.94, 68.82) --
	( 73.86, 68.82) --
	( 78.79, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 86.94) --
	( 86.99,108.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 86.99, 52.07) --
	( 86.99, 34.79) --
	( 86.99,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 82.07, 86.94) --
	( 82.07, 52.07) --
	( 86.99, 52.07) --
	( 91.92, 52.07) --
	( 91.92, 86.94) --
	( 86.99, 86.94) --
	( 82.07, 86.94) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 82.07, 68.82) --
	( 86.99, 68.82) --
	( 91.92, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 87.86) --
	(100.13,109.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.13, 52.07) --
	(100.13, 34.79) --
	(100.13,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 95.20, 87.86) --
	( 95.20, 52.07) --
	(100.13, 52.07) --
	(105.05, 52.07) --
	(105.05, 87.86) --
	(100.13, 87.86) --
	( 95.20, 87.86) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 95.20, 69.46) --
	(100.13, 69.46) --
	(105.05, 69.46);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 88.21) --
	(113.26,110.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.26, 52.23) --
	(113.26, 34.65) --
	(113.26,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (108.34, 88.21) --
	(108.34, 52.23) --
	(113.26, 52.23) --
	(118.18, 52.23) --
	(118.18, 88.21) --
	(113.26, 88.21) --
	(108.34, 88.21) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (108.34, 69.19) --
	(113.26, 69.19) --
	(118.18, 69.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 87.91) --
	(126.39,110.12);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.39, 51.43) --
	(126.39, 34.23) --
	(126.39,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (121.47, 87.91) --
	(121.47, 51.43) --
	(126.39, 51.43) --
	(131.32, 51.43) --
	(131.32, 87.91) --
	(126.39, 87.91) --
	(121.47, 87.91) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (121.47, 68.82) --
	(126.39, 68.82) --
	(131.32, 68.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 89.24) --
	(139.53,111.73);

\path[draw=drawColor,line width= 0.6pt,line join=round] (139.53, 51.43) --
	(139.53, 34.51) --
	(139.53,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (134.60, 89.24) --
	(134.60, 51.43) --
	(139.53, 51.43) --
	(144.45, 51.43) --
	(144.45, 89.24) --
	(139.53, 89.24) --
	(134.60, 89.24) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (134.60, 69.28) --
	(139.53, 69.28) --
	(144.45, 69.28);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 88.81) --
	(152.66,111.09);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.66, 51.92) --
	(152.66, 35.33) --
	(152.66,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (147.73, 88.81) --
	(147.73, 51.92) --
	(152.66, 51.92) --
	(157.58, 51.92) --
	(157.58, 88.81) --
	(152.66, 88.81) --
	(147.73, 88.81) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (147.73, 69.37) --
	(152.66, 69.37) --
	(157.58, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 89.53) --
	(165.79,112.08);

\path[draw=drawColor,line width= 0.6pt,line join=round] (165.79, 51.43) --
	(165.79, 34.09) --
	(165.79,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (160.87, 89.53) --
	(160.87, 51.43) --
	(165.79, 51.43) --
	(170.72, 51.43) --
	(170.72, 89.53) --
	(165.79, 89.53) --
	(160.87, 89.53) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (160.87, 69.19) --
	(165.79, 69.19) --
	(170.72, 69.19);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 89.53) --
	(178.92,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (178.92, 51.60) --
	(178.92, 40.77) --
	(178.92, 24.09) --
	(178.92,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (174.00, 89.53) --
	(174.00, 51.60) --
	(178.92, 51.60) --
	(183.85, 51.60) --
	(183.85, 89.53) --
	(178.92, 89.53) --
	(174.00, 89.53) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (174.00, 69.64) --
	(178.92, 69.64) --
	(183.85, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 89.63) --
	(192.06,112.20);

\path[draw=drawColor,line width= 0.6pt,line join=round] (192.06, 51.43) --
	(192.06, 34.51) --
	(192.06,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (187.13, 89.63) --
	(187.13, 51.43) --
	(192.06, 51.43) --
	(196.98, 51.43) --
	(196.98, 89.63) --
	(192.06, 89.63) --
	(187.13, 89.63) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (187.13, 69.64) --
	(192.06, 69.64) --
	(196.98, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 90.11) --
	(205.19,112.82);

\path[draw=drawColor,line width= 0.6pt,line join=round] (205.19, 51.27) --
	(205.19, 33.95) --
	(205.19,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (200.27, 90.11) --
	(200.27, 51.27) --
	(205.19, 51.27) --
	(210.11, 51.27) --
	(210.11, 90.11) --
	(205.19, 90.11) --
	(200.27, 90.11) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (200.27, 69.37) --
	(205.19, 69.37) --
	(210.11, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 90.05) --
	(218.32,112.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (218.32, 51.11) --
	(218.32, 34.09) --
	(218.32,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (213.40, 90.05) --
	(213.40, 51.11) --
	(218.32, 51.11) --
	(223.25, 51.11) --
	(223.25, 90.05) --
	(218.32, 90.05) --
	(213.40, 90.05) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (213.40, 69.00) --
	(218.32, 69.00) --
	(223.25, 69.00);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 90.34) --
	(231.46,112.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (231.46, 51.27) --
	(231.46, 34.51) --
	(231.46,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (226.53, 90.34) --
	(226.53, 51.27) --
	(231.46, 51.27) --
	(236.38, 51.27) --
	(236.38, 90.34) --
	(231.46, 90.34) --
	(226.53, 90.34) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (226.53, 69.37) --
	(231.46, 69.37) --
	(236.38, 69.37);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 90.24) --
	(244.59,112.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] (244.59, 51.60) --
	(244.59, 34.79) --
	(244.59,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (239.66, 90.24) --
	(239.66, 51.60) --
	(244.59, 51.60) --
	(249.51, 51.60) --
	(249.51, 90.24) --
	(244.59, 90.24) --
	(239.66, 90.24) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (239.66, 69.64) --
	(244.59, 69.64) --
	(249.51, 69.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 90.95) --
	(257.72,113.87);

\path[draw=drawColor,line width= 0.6pt,line join=round] (257.72, 51.11) --
	(257.72, 33.95) --
	(257.72,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (252.80, 90.95) --
	(252.80, 51.11) --
	(257.72, 51.11) --
	(262.65, 51.11) --
	(262.65, 90.95) --
	(257.72, 90.95) --
	(252.80, 90.95) --
	cycle;

>>>>

% Created by tikzDevice version 0.12.3 on 2020-01-21 13:23:35
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,144.54);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,144.54);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( -0.00,  0.00) rectangle (433.62,144.54);
\end{scope}
\begin{scope}
\path[clip] ( 22.14, 19.53) rectangle (430.12,141.04);
\definecolor{fillColor}{gray}{0.92}

\path[fill=fillColor] ( 22.14, 19.53) rectangle (430.12,141.04);
\definecolor{drawColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14, 79.39) --
	(430.12, 79.39);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14,113.42) --
	(430.12,113.42);

\path[draw=drawColor,line width= 0.2pt,line join=round] ( 22.14,122.92) --
	(430.12,122.92);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 22.14, 19.53) --
	(430.12, 19.53);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 22.14,100.38) --
	(430.12,100.38);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 35.42, 19.53) --
	( 35.42,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 49.04, 19.53) --
	( 49.04,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 62.67, 19.53) --
	( 62.67,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 76.29, 19.53) --
	( 76.29,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] ( 89.91, 19.53) --
	( 89.91,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (103.53, 19.53) --
	(103.53,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (117.15, 19.53) --
	(117.15,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (130.78, 19.53) --
	(130.78,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (144.40, 19.53) --
	(144.40,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (158.02, 19.53) --
	(158.02,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (171.64, 19.53) --
	(171.64,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (185.26, 19.53) --
	(185.26,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (198.89, 19.53) --
	(198.89,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (212.51, 19.53) --
	(212.51,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (226.13, 19.53) --
	(226.13,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (239.75, 19.53) --
	(239.75,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (253.37, 19.53) --
	(253.37,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (267.00, 19.53) --
	(267.00,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (280.62, 19.53) --
	(280.62,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (294.24, 19.53) --
	(294.24,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (307.86, 19.53) --
	(307.86,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (321.48, 19.53) --
	(321.48,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (335.11, 19.53) --
	(335.11,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (348.73, 19.53) --
	(348.73,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (362.35, 19.53) --
	(362.35,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (375.97, 19.53) --
	(375.97,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (389.59, 19.53) --
	(389.59,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (403.22, 19.53) --
	(403.22,141.04);

\path[draw=drawColor,line width= 0.4pt,line join=round] (416.84, 19.53) --
	(416.84,141.04);
\definecolor{drawColor}{gray}{0.20}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 77.89) --
	( 35.42,100.83);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 35.42, 44.22) --
	( 35.42, 32.09) --
	( 35.42, 13.41) --
	( 35.42,  0.00);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 30.31, 77.89) --
	( 30.31, 44.22) --
	( 35.42, 44.22) --
	( 40.53, 44.22) --
	( 40.53, 77.89) --
	( 35.42, 77.89) --
	( 30.31, 77.89) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 30.31, 61.34) --
	( 35.42, 61.34) --
	( 40.53, 61.34);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.04, 80.95) --
	( 49.04,104.79);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 49.04, 44.22) --
	( 49.04, 25.49) --
	( 49.04,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 43.94, 80.95) --
	( 43.94, 44.22) --
	( 49.04, 44.22) --
	( 54.15, 44.22) --
	( 54.15, 80.95) --
	( 49.04, 80.95) --
	( 43.94, 80.95) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 43.94, 61.98) --
	( 49.04, 61.98) --
	( 54.15, 61.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.67, 81.37) --
	( 62.67,105.47);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 62.67, 43.33) --
	( 62.67, 23.51) --
	( 62.67,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 57.56, 81.37) --
	( 57.56, 43.33) --
	( 62.67, 43.33) --
	( 67.77, 43.33) --
	( 67.77, 81.37) --
	( 62.67, 81.37) --
	( 57.56, 81.37) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 57.56, 62.29) --
	( 62.67, 62.29) --
	( 67.77, 62.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.29, 82.62) --
	( 76.29,107.07);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 76.29, 43.51) --
	( 76.29, 24.13) --
	( 76.29,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 71.18, 82.62) --
	( 71.18, 43.51) --
	( 76.29, 43.51) --
	( 81.40, 43.51) --
	( 81.40, 82.62) --
	( 76.29, 82.62) --
	( 71.18, 82.62) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 71.18, 62.29) --
	( 76.29, 62.29) --
	( 81.40, 62.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.91, 83.65) --
	( 89.91,108.35);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.91, 43.51) --
	( 89.91, 24.13) --
	( 89.91,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 84.80, 83.65) --
	( 84.80, 43.51) --
	( 89.91, 43.51) --
	( 95.02, 43.51) --
	( 95.02, 83.65) --
	( 89.91, 83.65) --
	( 84.80, 83.65) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 84.80, 63.01) --
	( 89.91, 63.01) --
	( 95.02, 63.01);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.53, 84.04) --
	(103.53,108.80);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.53, 43.69) --
	(103.53, 23.97) --
	(103.53,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] ( 98.42, 84.04) --
	( 98.42, 43.69) --
	(103.53, 43.69) --
	(108.64, 43.69) --
	(108.64, 84.04) --
	(103.53, 84.04) --
	( 98.42, 84.04) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] ( 98.42, 62.70) --
	(103.53, 62.70) --
	(108.64, 62.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.15, 83.71) --
	(117.15,108.60);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.15, 42.80) --
	(117.15, 23.51) --
	(117.15,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (112.05, 83.71) --
	(112.05, 42.80) --
	(117.15, 42.80) --
	(122.26, 42.80) --
	(122.26, 83.71) --
	(117.15, 83.71) --
	(112.05, 83.71) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (112.05, 62.29) --
	(117.15, 62.29) --
	(122.26, 62.29);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.78, 85.20) --
	(130.78,110.42);

\path[draw=drawColor,line width= 0.6pt,line join=round] (130.78, 42.80) --
	(130.78, 23.82) --
	(130.78,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (125.67, 85.20) --
	(125.67, 42.80) --
	(130.78, 42.80) --
	(135.88, 42.80) --
	(135.88, 85.20) --
	(130.78, 85.20) --
	(125.67, 85.20) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (125.67, 62.81) --
	(130.78, 62.81) --
	(135.88, 62.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.40, 84.71) --
	(144.40,109.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (144.40, 43.33) --
	(144.40, 24.74) --
	(144.40,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (139.29, 84.71) --
	(139.29, 43.33) --
	(144.40, 43.33) --
	(149.51, 43.33) --
	(149.51, 84.71) --
	(144.40, 84.71) --
	(139.29, 84.71) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (139.29, 62.91) --
	(144.40, 62.91) --
	(149.51, 62.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.02, 85.52) --
	(158.02,110.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.02, 42.80) --
	(158.02, 23.35) --
	(158.02,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (152.91, 85.52) --
	(152.91, 42.80) --
	(158.02, 42.80) --
	(163.13, 42.80) --
	(163.13, 85.52) --
	(158.02, 85.52) --
	(152.91, 85.52) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (152.91, 62.70) --
	(158.02, 62.70) --
	(163.13, 62.70);

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.64, 85.52) --
	(171.64,110.65);

\path[draw=drawColor,line width= 0.6pt,line join=round] (171.64, 42.98) --
	(171.64, 30.84) --
	(171.64, 12.13) --
	(171.64,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (166.53, 85.52) --
	(166.53, 42.98) --
	(171.64, 42.98) --
	(176.75, 42.98) --
	(176.75, 85.52) --
	(171.64, 85.52) --
	(166.53, 85.52) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (166.53, 63.21) --
	(171.64, 63.21) --
	(176.75, 63.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.26, 85.63) --
	(185.26,110.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.26, 42.80) --
	(185.26, 23.82) --
	(185.26,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (180.16, 85.63) --
	(180.16, 42.80) --
	(185.26, 42.80) --
	(190.37, 42.80) --
	(190.37, 85.63) --
	(185.26, 85.63) --
	(180.16, 85.63) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (180.16, 63.21) --
	(185.26, 63.21) --
	(190.37, 63.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.89, 86.17) --
	(198.89,111.64);

\path[draw=drawColor,line width= 0.6pt,line join=round] (198.89, 42.61) --
	(198.89, 23.19) --
	(198.89,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (193.78, 86.17) --
	(193.78, 42.61) --
	(198.89, 42.61) --
	(203.99, 42.61) --
	(203.99, 86.17) --
	(198.89, 86.17) --
	(193.78, 86.17) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (193.78, 62.91) --
	(198.89, 62.91) --
	(203.99, 62.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.51, 86.11) --
	(212.51,111.59);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.51, 42.43) --
	(212.51, 23.35) --
	(212.51,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (207.40, 86.11) --
	(207.40, 42.43) --
	(212.51, 42.43) --
	(217.62, 42.43) --
	(217.62, 86.11) --
	(212.51, 86.11) --
	(207.40, 86.11) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (207.40, 62.50) --
	(212.51, 62.50) --
	(217.62, 62.50);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.13, 86.42) --
	(226.13,111.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (226.13, 42.61) --
	(226.13, 23.82) --
	(226.13,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (221.02, 86.42) --
	(221.02, 42.61) --
	(226.13, 42.61) --
	(231.24, 42.61) --
	(231.24, 86.42) --
	(226.13, 86.42) --
	(221.02, 86.42) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (221.02, 62.91) --
	(226.13, 62.91) --
	(231.24, 62.91);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.75, 86.32) --
	(239.75,111.71);

\path[draw=drawColor,line width= 0.6pt,line join=round] (239.75, 42.98) --
	(239.75, 24.13) --
	(239.75,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (234.64, 86.32) --
	(234.64, 42.98) --
	(239.75, 42.98) --
	(244.86, 42.98) --
	(244.86, 86.32) --
	(239.75, 86.32) --
	(234.64, 86.32) --
	cycle;

\path[draw=drawColor,line width= 1.1pt,line join=round] (234.64, 63.21) --
	(239.75, 63.21) --
	(244.86, 63.21);

\path[draw=drawColor,line width= 0.6pt,line join=round] (253.37, 87.11) --
	(253.37,112.81);

\path[draw=drawColor,line width= 0.6pt,line join=round] (253.37, 42.43) --
	(253.37, 23.19) --
	(253.37,  0.00);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (248.27, 87.11) --
	(248.27, 42.43) --
	(253.37, 42.43) --
	(258.48, 42.43) --
	(258.48, 87.11) --
	(253.37, 87.11) --
	(248.27, 87.11) --
	cycle;
